\thetitle

### 2013-04-17 tfpie/tfpie.tex
Small touch ups.

On the first day of the second semester, we introduce a single
linguistic concept to an otherwise unchanged context of the previous
semester.

An object is a new kind of value that can, as a first cut, be
understood as a pairing together of two familiar concepts: data and
functionality.

@@

\item An object is like a (set of) function(s) in that it has behavior—it computes; it is
not just inert data.
\end{itemize}

This suggests that objects are a natural ﬁt for well-designed programs
since good programs are organized around data definitions and
functions that operate over such data. An object, in essence, packages
these two things together into a single programming apparatus. This
has two important consequences:

@@

Since objects are just the combination of two familiar concepts that
students already use to design programs, they already know how to
design programs around objects, even if they have never heard the term
``object'' before. Our message is the better you are at programming
with functions, the better you will be at programming with objects,
and \emph{vice versa}.

@@

Although the combination of data and function may seem simple, objects
enable new forms of abstraction and composition. That is, objects open
up new approaches to the construction of computations. By studying
these new approaches, we can distill new design principles. Because we
understand objects are just the combination of data and function, we
can understand how all of these principles apply in the familiar
context of programming with functions. In short, the better you are at
programming with objects, the better you will be at programming with
functions.

>>>>

On the first day of the second semester, we introduce a single
linguistic concept to an otherwise unchanged context of the previous
semester: the idea of an object.
%
An object is a new kind of value that can, as a first cut, be
understood as a pairing together of two familiar concepts: data and
functionality.

@@

\item An object is like a (set of) function(s) in that it has behavior---it computes; it is
not just inert data.
\end{itemize}

This suggests that objects are a natural fit for well-designed programs
since good programs are organized around data definitions and
functions that operate over such data. An object, in essence, packages
these two things together into a single programming apparatus. This
has two important consequences:

@@

Since objects are just the combination of two familiar concepts that
students already use to design programs, they already know how to
design programs around objects, even if they have never heard the term
``object'' before.

@@

Although the combination of data and functionality may seem simple,
objects enable new forms of abstraction and composition. That is,
objects open up new approaches to the construction of computations. By
studying these new approaches, we can distill new design
principles. Because we understand objects are just the combination of
data and functionality, we can understand how all of these principles
apply in the familiar context of programming with functions. In short,
the better you are at programming with objects, the better you will be
at programming with functions, and \emph{vice versa}.
